Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-13 src/dev_scale-grid/scale-grid.Rmd
It's the covariance matrix not Hessian that is reconstructed

```{r cov-reconstruction, class.source = 'fold-hide', fig.cap="Hessian matrix recons."}
E_s <- E[, 1:s]
Lambda_s <- Lambda[1:s, 1:s]
C_s <- E_s %*% Lambda_s %*% t(E_s)

>>>>

```{r cov-reconstruction, class.source = 'fold-hide', fig.cap="Covariance matrix reconstruction."}
E_s <- E[, 1:s]
Lambda_s <- Lambda[1:s, 1:s]
C_s <- E_s %*% Lambda_s %*% t(E_s)

### 2023-07-13 src/docs_21-06-23-mlgh/21-06-23-mlgh.Rmd
It's the covariance matrix not Hessian that is reconstructed

```{r, echo=FALSE, message=FALSE, fig.cap="If you reconstruct the Hessian with just those 8 dimensions, it looks pretty similar.", out.width = '90%'}
knitr::include_graphics("depends/reduced-rank-plot.png")
```

>>>>

```{r, echo=FALSE, message=FALSE, fig.cap="If you reconstruct the covariance matrix with just those 8 dimensions, it looks pretty similar.", out.width = '90%'}
knitr::include_graphics("depends/reduced-rank-plot.png")
```

### 2023-07-13 src/docs_paper/appendix.Rmd
It's the covariance matrix not Hessian that is reconstructed

```{r reduced-rank, fig.cap="The reduced rank (8) matrix approximation to the Hessian is visually similar to the full rank matrix."}
knitr::include_graphics("depends/reduced-rank.png")
```

>>>>

```{r reduced-rank, fig.cap="The reduced rank (8) matrix approximation to the covariance matrix is visually similar to the full rank original."}
knitr::include_graphics("depends/reduced-rank.png")
```
